---
title: "Metapopulation model"
author: "Odin Rumianowski"
date: "2024-03-22"
output :
  html_document :
    toc : yes
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache = FALSE)
```


```{r}
library(tidyverse)
library(ggplot2)
library(MCMCvis)
library(knitr)
library(patchwork)
library(hrbrthemes)
```

# Model version 

Priors sur la probabilité de détections

--

Pour les nestlings et les prebreeders

  p <- 0

Pour les Breeders

  LR
    p ~ dunif(0, 0.3)
    
  Satellites
    p ~ dunif(0, 0.7)
    
Pour les breeders sur les colonies et durant les années sans pression de lecture de bagues

  p <- 0
  

# Computational parameters

```{r}
comput_param = data.frame(ni=50000,
                          nb=10000,
                          nc=3,
                          nt=40,
                          na=4000)
colnames(comput_param)= c("Iterations", "Burning", "Nb. chains", "Thining", "Adaptative phase")

kable(comput_param)

```





```{r}
load(file = "out1_cmr_AE_v12_prior_p.Rda")
```


```{r}
estimates = c("Number of female fledging per pair in LR", "Number of female fledging per pair in small colonies",
              "Survival of adults", "Survival during the first year",
              "Breeding fidelity in LR", "Breeding fidelity in MA" , "Breeding fidelity in VE",
              "Breeding fidelity in V5", "Breeding fidelity in AE",
              "Natal fidelity in LR", "Natal fidelity in MA" , "Natal fidelity in VE",
              "Natal fidelity in V5", "Natal fidelity in AE",
              "Rate of accession to reproduction in LR", "Rate of accession to reproduction in small colonies"
              )
```


```{r}
cmr_peron = c(NA, NA, 0.828,0.273,0.830, 0.662, 0.803, 0.537, 0.954, 0.320, 0.429, 0.695, 0.713, 0.591, 0.716, 0.827)
integrated_peron = c(1.732, 0.605, 0.860, 0.213, 1, 0.626, 0.469, 0.373, 0.938, 0.392, 0.454, 0.722, 0.784, 0.301, 0.619, 0.846)
```

```{r}
my_cmr = c(NA, NA, out1$mean$phi[2], out1$mean$phi[1], out1$mean$breedingfidelity, out1$mean$natalfidelity, out1$mean$kappa) %>% round(., 3)
```


# Main parameters

```{r}
main_parameters = data.frame(cbind(estimates, cmr_peron, my_cmr,integrated_peron))
```


```{r}
kable(main_parameters)
```

## Dispersion
### Natal dispersion 

```{r}

col_dep = c("From LR", "From MA", "From VE", "From V5", "From AE")
col_arr = c(" ", "To LR", "To MA", "To VE", "To V5", "To AE")

```

```{r}
eta = out1$mean$eta_monitored %>% round(., 2)

eta = cbind(col_dep, eta)
eta = rbind(col_arr, eta)

```


```{r}
kable(eta, align = "c")
```

### Breeding dispersion

```{r}
nu = out1$mean$nu_monitored %>% round(., 2)

nu = cbind(col_dep, nu)
nu = rbind(col_arr, nu)

```


```{r}

kable(nu, align = "c")
```

## Recapture probability
           
In the analysis:

```{r}
p1 = out1$mean$po[6,] %>% 
  as.data.frame() %>%
  mutate(., val = .) %>% 
  ggplot(., aes(x =val)) +
  geom_histogram() +
  labs(title = "La Ronze")


p2 = out1$mean$po[7:9,] %>% 
  as.vector() %>% 
  as.data.frame() %>%
  mutate(., val = .) %>% 
  ggplot(., aes(x =val)) +
  geom_histogram()+
  labs(title = "Les satellites")

p3 = p1 + p2

p3

```


```{r}

x = paste0("", seq(1,19))
y = c("LR", "MA", "VE", "V5")
data <- expand.grid(Year=x, Colony=y)
data$p <- out1$mean$po[6:9,] %>% 
  as.data.frame() %>% 
  t() %>% 
  as.vector()

ggplot(data, aes(Year, Colony, fill= p)) + 
  geom_tile() +
  geom_text(aes(label = round(p, 1))) +
  scale_fill_gradient(low="white", high="blue") +
  hrbrthemes::theme_ipsum	()

```

# Traces
## Apparent survival probability


```{r}
PR_unif_01 <- runif(1E9, 0, 1)
```


```{r}
gvals = c(0.273, 0.830)

MCMCtrace(out1, params = c("phi"),
          Rhat = T,
          priors = PR_unif_01,
          gvals = gvals,
          ind = T, pdf = F,
          post_zm = F)

```



## Recruitment probability

```{r}


gvals = c(0.716, 0.827)

MCMCtrace(out1, params = c("kappa"),
          Rhat = TRUE,
          priors = PR_unif_01,
          gvals = gvals,
          ind = TRUE, pdf = FALSE,
          post_zm = F)


```


## Dispersion

### Traces of eta

```{r} 

MCMCtrace(out1, params = c("eta_monitored"),
          Rhat = TRUE,
          #priors = PR_unif_01,
          ind = TRUE, pdf = FALSE,
          post_zm = F)


```

### Traces of nu

```{r} 

MCMCtrace(out1, params = c("nu_monitored"),
          Rhat = TRUE,
          #priors = PR_unif_01,
          ind = TRUE, pdf = FALSE,
          post_zm = F)
```
